### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
Review of the text up to section 2.2 - Added few references for coalescence and p-Pb data, fixed typos in bib.

\usepackage[margin=2.5cm]{geometry}
\usepackage{multirow}
\usepackage{tabularx} 
\usepackage{rotating,graphicx} 
\usepackage{appendix} 
\usepackage{makecell}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath

%\ifpdf
%  \usepackage[pdftex]{graphicx}
%\else
%  \usepackage[dvips]{graphicx}
%\fi

@@

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions. Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they consequently largely differ in their description of (anti-)hyper-triton production.
%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. 
The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
\end{abstract}

@@

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm \cite{Nemura:1999qp} which is significantly larger than that of non-strange $A$ = 3 nuclei. This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm. In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.

Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}. 
In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}. Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease. Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances. Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically. At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects. For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement) \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}. 
Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is \textcolor{red}{smaller than the breakup cross-section} \cite{Schukraft:2017nbn}.   
Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}. 
\textcolor{red}{Do similar estimates as Karel in Frascati}. In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.

@@

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

To this purpose, we compare to models the existing data from the Large Hadron Collider. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;,    
\label{eq:BA}
\end{equation}

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.

@@

In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.

In particular, the wave-function of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$. For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

\noindent For larger nuclei (A > 2), analogous forms exist (see for instance~\cite{Scheibl:1998tk} for the explicit form of A=3). The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as

@@

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$. The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source (i.e. the centrality dependence) and the (hyper-)nucleus size. \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}

In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

>>>>

\usepackage[margin=2.5cm]{geometry}
\usepackage{multirow}
\usepackage{tabularx} 
\usepackage{rotating,graphicx} 
\usepackage{appendix} 
\usepackage{makecell}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{cite}
%\ifpdf
%  \usepackage[pdftex]{graphicx}
%\else
%  \usepackage[dvips]{graphicx}
%\fi

@@

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC). Their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions. Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. 
The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
\end{abstract}

@@

\section{Introduction} 
The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions. In addition, these studies might shed light on the internal structure of the formed objects themselves. 
In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e. the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.  
The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei. This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm \cite{Nemura:1999qp}. In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.

Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}. 
In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}. Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease. Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances. Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically. At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects. For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}. 
Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.   
Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}. 
%In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.

@@

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline \\[-2ex]
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\[1ex]  \hline \\[-2ex] 
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

To this purpose, we compare to models the existing data from the LHC. For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size. 
In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities. The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}. In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach. 
The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios. As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments. 
In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
,    
\label{eq:BA}
\end{equation}
anielski-HQ14
\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}. The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions. They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$. For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details). The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as

@@

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).

This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations. The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and that of the (hyper-)nucleus. In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.

The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
